The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-09-08 paper/Analisis.tex
New flux plots in anisotropic emission subsection

In Figure 2 we show the angular dependency of the flux for the
central (left) and homogeneous (right) source distributions. This
shows that observers at different directions would infer luminosities
different from the isotropical value only at levels $< 3\%$.

>>>>

In Figure \ref{fig:flux} we show the angular dependency of the flux for the
central (left) and homogeneous (right) source distributions. This
shows that observers at different directions would infer luminosities
different from the isotropical value only at levels $< 3\%$.

\begin{figure*}
\includegraphics[scale=0.3]{mu_central.png}
\includegraphics[scale=0.3]{mu_homogeneous.png}
\caption{Flux angular dependency for the central (left) and homogeneous
(right) source distributions, different line widths illustrate different
rotational velocities.
   \label{fig:flux}} 
\end{figure*}
